Fast approximate Bayesian inference of HIV indicators using the Naomi small-area estimation model

### 2023-06-18 src/docs_paper/paper.Rmd
Title change

---
title: Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model
author:
  - name: Adam 
    surname: Howes
    email: ath19@ic.ac.uk
    label: e1
    addressLabel: A,E
    sepNext: ","
  - name: Alex
    surname: Stringer
    email: alex.stringer@uwaterloo.ca
    label: e2
    addressLabel: B
  - name: Seth R.
    surname: Flaxman
    email: seth.flaxman@cs.ox.ac.uk
    label: e3
    addressLabel: C
    sepNext: ","
  - name: Jeffrey W.
    surname: Eaton
    email: jeaton@hsph.harvard.edu
    label: e4
    addressLabel: D,E
affiliation:
  - label: A
    name: Department of Mathematics, Imperial College London
    authorsLabels: e1
  - label: B
    name: Department of Statistics and Actuarial Science, University of Waterloo
    authorsLabels: e2
  - label: C
    name: Department of Computer Science, University of Oxford
    authorsLabels: e3
  - label: D
    name: Center for Communicable Disease Dynamics, Harvard T.H. Chan School of Public Health, Harvard University
    authorsLabels: e4
  - label: E
    name: MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial College London

>>>>

---
title: Fast approximate Bayesian inference of HIV indicators using the Naomi small-area estimation model
author:
  - name: Adam 
    surname: Howes
    email: ath19@ic.ac.uk
    label: e1
    addressLabel: A,E
    sepNext: ","
  - name: Alex
    surname: Stringer
    email: alex.stringer@uwaterloo.ca
    label: e2
    addressLabel: B
  - name: Seth R.
    surname: Flaxman
    email: seth.flaxman@cs.ox.ac.uk
    label: e3
    addressLabel: C
    sepNext: ","
  - name: Jeffrey W.
    surname: Eaton
    email: jeaton@hsph.harvard.edu
    label: e4
    addressLabel: D,E
affiliation:
  - label: A
    name: Department of Mathematics, Imperial College London
    authorsLabels: e1
  - label: B
    name: Department of Statistics and Actuarial Science, University of Waterloo
    authorsLabels: e2
  - label: C
    name: Department of Computer Science, University of Oxford
    authorsLabels: e3
  - label: D
    name: Center for Communicable Disease Dynamics, Harvard T.H. Chan School of Public Health, Harvard University
    authorsLabels: e4
  - label: E
    name: MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial College London
